Legacy Data Confounds Modern Genomics Studies

### 2019-03-24 PlottingScripts/ProcessPlotData.Rmd
update

load libraries
```{r, message = FALSE}
library(ggplot2)
library(RColorBrewer)
library(plotly)
library(colorspace)
library(cowplot)
library(data.table)
library(tidyverse)
library(purrr)

@@

SNP
INDEL
```
##Compare Over and Under Qual 30
```{r}
#read Genotypes
GT = fread(paste0(DataPath,
                   'SigVar_Pop_0.01_rsID.genotype.txt'))
ColNames = read.table(paste0(DataPath,
                   'ColNames_rsID.txt'), 
                   header=F)

>>>>

load libraries
```{r, message = FALSE}
library(ggplot2)
library(RColorBrewer)
library(plotly)
library(colorspace)
library(cowplot)
library(data.table)
library(tidyverse)
library(purrr)
library(lfa)

@@

SNP
INDEL
```
##Extract Significant Positions from 1kGP Data
```{bash}
DataPath='/Users/luke/Documents/QualityPaper/ProcessedData'
RawDataPath='/Users/luke/genomes/genomes/hg19/phase3'
VCF='.phase3_shapeit2_mvncall_integrated_v5a.20130502.genotypes.vcf.gz'

#GetHeader
zgrep '^#' $RawDataPath/ALL.chr22$VCF > $DataPath/Significant_Positions.vcf

#AddGenotypes
for f in `seq 1 22`;
do echo $f;
bcftools view -R $DataPath/Significant_Positions.txt \
$RawDataPath/ALL.chr${f}$VCF \
| grep -v "^#" \
>> $DataPath/Significant_Positions.vcf ; \
done

#bcftools doesn't take rsID
#this deals with indels and other mulitallelic variants
vcftools \
--vcf $DataPath/Significant_Positions.vcf \
--snps $DataPath/Significant_rsID.txt \
--recode --recode-INFO-all \
--out $DataPath/Significant_Positions

/Users/luke/bin/plink_mac/plink \
--vcf $DataPath/Significant_Positions.recode.vcf \
--recode \
--out $DataPath/Significant_Positions

```
```{r}
data_bim <- fread(paste0(DataPath,
                         'Significant_Positions.bim'), 
                  col.names = c('Chr','rsID','X',
                                'Pos','Ref','Alt')) %>%
  select(rsID)

data_fam <- fread(paste0(DataPath,
                         'Significant_Positions.fam'), 
                  col.names = c('familyID','sample',
                                'father','mother',
                                'sex','pheno')) %>%
  select(sample)

data_genotype <- read.bed(paste0(DataPath,'Significant_Positions'))
rownames(data_genotype) <- data_bim$rsID
colnames(data_genotype) <- data_fam$sample
data_genotype[1:5,1:5]

```

##Compare Over and Under Qual 30
```{r}
#read Genotypes
GT = fread(paste0(DataPath,
                   'SigVar_Pop_0.01_rsID.genotype.txt'))
ColNames = read.table(paste0(DataPath,
                   'ColNames_rsID.txt'), 
                   header=F)
